Backpropagating Gravitational wave events

### 2022-04-19 src/ms.tex
update

To summarize, we propose a novel method to recover the posterior samples in the evolutionary parameter space for each GW event.
We point out hyper-parameters in the usual population synthesis simulation context are not actually parameters related to the population,
but parameters about the evolutionary function.
This means the binary evolution functions can be constrained on an individual event basis.
We "back propagate" the posterior in the observable space to the evolutionary parameter space,
thus allowing us to study hyper-parameters and its correlation with progenitor parameters in a data-driven manner.
Our method makes less assumption than the traditional forward modelling approach,
which often fix the hyper-parameters across the entire population.
Since we are not limited to the fix hyper-parameters assumption, we can explore the behavior of the hyper-parameters across the population much more efficiently.
While our work lay down a data analysis pathway to understand the population of GW events,
no physics can be learned without a comprehensive complimentary physical model.
We hope this letter would motivate the community to build the next generation population synthesis codes that have the following properties:
first, they should have explicit control over the random variables so marginalizing over random variables can be done more precisely;
second, they should be as automatically differentiable as much as possible so exploring the evolutionary parameter space is efficient.
Combining this work and the next generation population synthesis code,
we can explore the full parameter space of binary evolution models with the next-generation GW detectors network in the near future.

>>>>

To summarize, we propose a novel method to recover the posterior samples in the evolutionary parameter space for each GW event.
We point out hyper-parameters in the usual population synthesis simulation context are not actually parameters related to the population,
but parameters about the evolutionary function.
This means the binary evolution functions can be constrained on an individual event basis.
We "back propagate" the posterior in the observable space to the evolutionary parameter space,
thus allowing us to study hyper-parameters and its correlation with progenitor parameters in a data-driven manner.
Our method makes less assumption than the traditional forward modelling approach,
which often fix the hyper-parameters across the entire population.
Since we are not limited to the fix hyper-parameters assumption, we can explore the behavior of the hyper-parameters across the population much more efficiently.
While our work lay down a data analysis pathway to understand the population of GW events,
no physics can be learned without a comprehensive physical model.
We hope this letter would motivate the community to build the next generation population synthesis codes that have the following properties:
first, they should have explicit control over the random variables so marginalizing over random variables can be done more precisely;
second, they should be as automatically differentiable as much as possible so exploring the evolutionary parameter space is efficient.
Combining this work and the next generation population synthesis code,
we can explore the full parameter space of binary evolution models with the next-generation GW detectors network in the near future.
